\subsection{Primary types - Association types descriptions}




The table below is providing comments on the association types of the primary types.

\begin{associationtypes}
\addheading{Undirected associations}
\adddoublerow{assctAlertctCrisis}{a crisis is related to one or more alerts as the alerts judged to concern all the same crisis due to their location. An alert alerts exactly one crisis.}
\adddoublerow{assctAlertctHuman}{ alerts are notified by human through the communication company. We need to keep an internal representation of those human to allow for communication of alert handling.}
\adddoublerow{assctAuthenticatedactAuthenticated}{mainly used to determine if the login request of an authenticated actor can be granted based on the given credentials and the registered ones.}
\adddoublerow{assctComCompanyactComCompany}{in order to associate the added human to communication company, which send them messages. For selection communication company this association is necessary, it let us select actComCompany by id of ctComCompany.}
\adddoublerow{assctCoordinatoractCoordinator}{frequent messages must be sent to coordinator especially in relation to crisis they handle.}
\adddoublerow{assctCrisisctCoordinator}{at any point in time we need to know if a coordinator is handling existing crisis or not.}
\adddoublerow{assctHumanactComCompany}{ in order to communicate with humans who informed about potential crisis, we need to record the communication company to use to send them messages.}
\adddoublerow{assctHumanFamilyctCrisis}{a family member (human) is related to one or more crisis. An crisis can be related to zero or more family members.}
\end{associationtypes}
